---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dkbi

A general purpose package for Dankegongyu business intelligence unit. 

## Installation

You can install the development version of dkbi from internal RStudio package manager.

``` r
install.packages("dkbi", repos = "<internal-cran>")
```

## Required Variables

By default, `dkbi` will look for an `consul` object in your R global environment. It is recommended to set the following system variables in your `.Renviron` file.

```{r, eval=FALSE}
consul.host = "some host"
consul.port = "some port"
consul.swagger = "some swagger"
consul.secret = "some secret"
```

## Common Workflow

`dkbi` helps to fetch values from KV store and make connection to databases.

```{r example, eval=FALSE}
library(dkbi)

# initiate config.R to specific path
init_config(path = "R/")

# source configs
source("R/config.R")

# make connection to database
est_mysql_conn("Forecast")
```

```bash
<MySQLConnection:0,0>
```

```{r, eval=FALSE}
# fetch parameters from KV store
get_batch_kv("some_api_params", "host", "port", "swagger")
```

```bash
$host
[1] "some_api_host"

$port
[1] "some_api_port"

$swagger
[1] "some_api_swagger"
```

## Available Commands

```{r}
library(dkbi)
ls('package:dkbi')
```



